---
title: "R Notebook"
output: html_notebook
---

##Chpaters 4 and exercises

```{r}
1 / 200 * 30
(59+73+2)/3
sin(pi/2)

```

Create new objects by using _<-_
```{r}
x <- 3*4
```

All R statements, when you create objects, have the same format: 

Reminder: Use spaces between assingments and use of _<-_

object names need to strat with a letter and can only have letters, numbers, periods, and underscores. Make it descriptive as possible by adding periods or snake case. 
```{r}
x 
```
```{r}
this_is_a_really_long_name <- 3.5
this_is_a_really_long_name
```
```{r}
r_rocks <- 2 ^ 3
r_rocks
```
R will not recognize the object if you misspell, use typos, or the wrong case. 
```{r}
seq(1,10)
x <- "hello world"
```


The plus sign _+_ tell you that R is waiting for more input. In most cases it means that you forgot and paired quotation mark or a parentheses. 
```{r}
y <- seq(1,10, length.out = 5)
y
```

This action can be shortened by surrounding the assignment with parentheses. 
```{r}
(y <- seq(1, 10, length.out = 5))
```

In the upper right pane, the environment tab, you can see all the objects you create as you go and hit run. 

##Practice
1. 
```{r}
my_variable <- 10 

```
It does not work because the "i" is  typed wrong. 

2. 

```{r}
library(tidyverse)

ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3) 
```



3. 
You can get to the shortcuts by clicking on the tools tab and there is a Keyboard Shortcuts Help. 

##Chapter 6 Practice 
1. 
Using cmd + alt + shift + M is a shortcut to rename variable names within RScript. 

2. 
Other common mistakes RStudio will report is checking arguments, it can detect missing arguments, unmatched arguments, partially matched arguments, and too many arguments. It can also warn you if a symbol is used with no difinition and the disgnostics engine supplies a suggestion. It will also warn you if a variable is defined but used and this can help clean the old code or help in diagnosing other errors (where you believe a particular variable should be used, but isn't).  